Bayesian Neural Networks

### 2024-05-06 Paper/paper.tex
removed abstract
lol
More discussion of hyperparameters

\begin{abstract}
	Bayesian Neural Networks are...
\end{abstract}

@@

\subsection{Neural Network Training}

To train a neural network requires a loss function $L$, such as the MSE or the cross-entropy loss (cross-entropy loss is essentially the log-likelihood loss from frequentist maximum likelihood estimation). An optimization process, typically a variant of stochastic gradient descent, adjusts the neural network parameters $\beta$ (the weights $W$ and biases $b$) to minimize this loss on the provided data. Stochastic gradient descent updates the parameters at each step by the formula
$$
\beta_{n+1} = \beta_n - \alpha (\nabla \ell(x_s, y_s, \beta)),
$$
where $\alpha$ is the learning rate (how quickly parameter adjustments are made). Minimization is implemented using a stochastic approximation of the gradient of the loss (hence the name stochastic gradient descent). The true loss $L(\beta)$ on the whole dataset $x, y$ is approximated via an averaged estimate $\ell(x_s, y_s, \beta)$ on a subset $(x_s, y_s)$ of the data. Gradients are calculated via \textit{backpropagation}, which is beyond the scope of this discussion, but essentially consists of iterated application of the chain rule.

@@

% TODO: Fill in information about how distributions are imposed on a BNN

@@

\subsubsection{Priors}

@@

However, it turns out there is suggestive parallel between a prior in a Bayesian neural network and regularization in a typical neural network. Regularization is an additional term in the loss that penalizes large weights. Intuitively, this helps resist overfitting by preventing a single neuron from overly influencing the model, since such a neuron may be overemphasizing a fluke of the training set rather than a general pattern. The regularization term typically takes the form $\alpha ||w||_p$  where $||\cdot||_p$ is some choice of metric on $R^n$, typically $p=1$ (Manhattan/taxicab distance) or $p=2$ (Euclidean distance), and $\alpha$ is the regularization hyperparameter that controls how strongly large weights are penalized.

@@

@@

We use a BCNN implementation from \href{https://github.com/kumar-shridhar/PyTorch-BayesianCNN}{Github} based on work from ... \cite{shridhar2019comprehensive} \cite{shridhar2018uncertainty}

@@

\subsection{Hyperparamaters}

We choose to keep the number of layers and levels in the model the same to keep the models roughly equal, but tuned the hyperparamaters seperately. We did not adjust the priors on the BCNN, as those were set by the BCNN layer code from \cite{shridhar2018uncertainty}. We found the following hyperparemeters to created the best model:

>>>>

%\begin{abstract}
%	Bayesian Neural Networks are...
%\end{abstract}

@@

\subsection{Neural Network Training}
\label{subsection:neural-network-training}

To train a neural network requires a loss function $L$, such as the MSE or the cross-entropy loss (cross-entropy loss is essentially the log-likelihood loss from frequentist maximum likelihood estimation). An optimization process, typically a variant of stochastic gradient descent, adjusts the neural network parameters $\beta$ (the weights $W$ and biases $b$) to minimize this loss on the provided data. Stochastic gradient descent updates the parameters at each step by the formula
$$
\beta_{n+1} = \beta_n - \alpha (\nabla \ell(x_s, y_s, \beta)),
$$
where $\alpha$ is the \textit{learning rate}, which controls how quickly parameter adjustments are made. Minimization is implemented using a stochastic approximation of the gradient of the loss (hence the name stochastic gradient descent). The true loss $L(\beta)$ on the whole dataset $x, y$ is approximated via an averaged estimate $\ell(x_s, y_s, \beta)$ on a subset $(x_s, y_s)$ of the data. Gradients are calculated via \textit{backpropagation}, which is beyond the scope of this discussion, but essentially consists of iterated application of the chain rule.

@@

% TODO: Fill in information about how distributions are imposed on a BNN. See other TODO with some progress at the end of the following subsection(s)

@@

\subsubsection{Priors}
\label{subsection:priors}

@@

However, it turns out there is suggestive parallel between a prior in a Bayesian neural network and \textit{regularization} in a typical neural network. \textit{Regularization} is an additional term in the loss that penalizes large weights. Intuitively, this helps resist overfitting by preventing a single neuron from overly influencing the model, since such a neuron may be overemphasizing a fluke of the training set rather than a general pattern. The regularization term typically takes the form $\alpha ||w||_p$  where $||\cdot||_p$ is some choice of metric on $R^n$, typically $p=1$ (Manhattan/taxicab distance) or $p=2$ (Euclidean distance), and $\alpha$ is the regularization hyperparameter that controls how strongly large weights are penalized. In other words, $\alpha$ is the \textit{regularization rate}.

@@

% TODO: Add discussion of how distributions are imposed
%\subsection{Distributions}

%In order to impose distributions on the parameters of a Bayesian neural network, there must be a clearly defined procedure for producting a posterior from the prior and the data.

%Gradient descent is used to minimize (the approximation of) the KL-divergence...

@@

We use an implementation of BCNNs from \href{https://github.com/kumar-shridhar/PyTorch-BayesianCNN}{Github} based on work from \cite{shridhar2019comprehensive} \cite{shridhar2018uncertainty}. It allowed for direct substitution of Bayesian layers for deterministic neural network layers such that the same training procedure could be applied to both types of networks. The normal priors previously discussed are built into these custom layers in the package.

@@

\subsection{Hyperparameters}

The hyperparameters of a neural network, such as epochs, learning rate, regularization rate, are set before training to control the process and ensure the network achieves the best possible performance for its architecture. Epochs and learning rate were defined in Subsection \ref{subsection:neural-network-training} while the regularization rate and its connection to Bayesian network priors was introduced in \ref{subsection:priors}. The choice of optimizer is not relevant to and beyond the scope of this work - Adamw as selected here simply provides a marginal performance improvement.

We choose to keep the number of layers and levels in the model the same to keep the models roughly equal, but tuned the hyperparameters separately. We did not adjust the priors on the BCNN, as those were set by the BCNN layer code from \cite{shridhar2018uncertainty}. We found the following hyperparemeters created the best model:
